%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
    {}
    {Real-time questionnaire website (Web full stack)} % Project Summary
    {
      \textcolor{graytext}{Sep. 2017 - Dec. 2017}
    } % Date(s)
    {}
    {}

  \vspace{-15mm}
  \cventry
    {}
    {}
    {}
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a single-page application which allows users to collect survey results in real time}
        \item {Built responsive web, implemented for both mobile and web viewing cases utilizing HTML5 and CSS}
        \item {Used React, JavaScript for front-end components interaction and Express, Node.js for server side}
        \item {Deployed backend system on cloud infrastructure Heroku}
        \item {Implemented a set of Restful API to allow front-end components to write/read data with server}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {}
    {Event Posting \& Booking Android App (Java)} % Project Summary
    {
      \textcolor{graytext}{Jan. 2017 - Apr. 2017} % Date(s)
    }
    {}
    {}

  \vspace{-15mm}
  \cventry
    {}
    {}
    {}
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and built android app to post and reserve the events}
        \item {Set up accounts login using Google firebase}
        \item {Developed data management part, event list panel, user and event info item class}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {}
    {Ticket SQL database for Microsoft exchange support group  (SQL Server)} % Project Summary
    {
      \textcolor{graytext}{Oct. 2016 - Nov. 2016} % Date(s)
    }
    {}
    {}

  \vspace{-15mm}
  \cventry
    {}
    {}
    {}
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Discussed with sponsors about the requirements and designed Entity Relationship Models based on that}
        \item {Designed databases to analysis tickets’ source and to generate reports to measure team performance}
        \item {Implemented the database using SQL server by creating tables, stored procedures and functions}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {}
    {Vehicle Dealer Management System (Java, Swing)} % Project Summary
    {
      \textcolor{graytext}{Oct. 2016 - Dec. 2016} % Date(s)
    }
    {}
    {}

  \vspace{-15mm}
  \cventry
    {}
    {}
    {}
    {}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked with other teams (25 people) to design the functionality and to implement UI using Swing}
        \item {Designed and Implemented a sort panel that in-time updates product order according to user inputs}
        \item {Tested the APIs (sort/search/reading file/writing file) and managed to finish milestones timely}
      \end{cvitems}
    }
  \vspace{-2mm}


%---------------------------------------------------------
\end{cventries}
